Do motif roles provide unique information about species risk of extinction?\\ \medskip Supplementary Information

### 2021-07-08 manuscript/supplement_motifs.tex
Updates from Overleaf

@@

    \subsection*{Degree and trophic level}

>>>>

    \subsection*{Methods}

        As one more level of detail, we can consider the frequency with which a species appears in each \emph{position} in each motif. 
        Different positions are associated with different numbers of predators and prey, making the similarities and differences between motifs and degree more explicit.
        The full set of these positions, across all motifs, is the species' \emph{motif role}~\citep{Stouffer2010,Cirtwill2017}.
        As with motif participation, we normalized motif roles by dividing the number of times a species appeared in each position by the total number of times it appeared in all positions~\citep{Baker2015,Cirtwill2017}.

        [[Could add a PERMANOVA to show that species' roles overal affect their persistence. Haven't done so yet.]]

        To test whether participating in different motif positions was related to a species' probability of persistence, we fit similar models to those for motif participation.
        For each position, we fit a linear mixed-effect model relating persistence to the frequency of the position in a species' motif role, disturbance, and their interaction.
        To account for differences in persistence across networks of different size and connectance, we included a random effect of the interaction between size and connectance.
        All regressions were fit using the R~\citep{R} function `lmer' from the package \emph{lmerTest}~\citep{lmerTest}.

    \subsection*{Results}

@@

    \subsection*{Methods}

        As with network motif profiles and motif participation, species' motif roles may vary with network size and connectance and with the species' in degree and trophic level.
        To identify these relationships, we fit two linear regressions for each motif position.
        The first related the frequency of the position in species' roles to network size, connectance, and their interaction.
        The second related the frequency of the position to in-degree, STL, and their interaction.
        All regressions were fit using the R~\citep{R} base function `lm'.

    \subsection*{Results}
        \subsection*{Degree and trophic level}
